\documentclass{article}

\begin{document}

\title{Personal Organizer with Machine Learning Optimization}
\author{Samuel Imboden}

\maketitle

\section{Description}

This project aims to create a personal organizer application that allows users to manage their work and household tasks in one central location. The application will use a REST API to connect the frontend and backend components and will be built using the Python programming language. For the database system, we will use Apache Cassandra, which provides scalability and performance for handling large amounts of data.

In addition, we plan to incorporate machine learning and AI to optimize the user's task management experience. We will use TensorFlow, a popular open-source machine learning library, to train models that can analyze the user's task history and provide personalized recommendations for task prioritization and scheduling.

The application will be deployed using Docker containers managed with Docker Compose,\\ which will provide scalability and manageability of the database cluster.

\section{Features}

\begin{itemize}
  \item Task management: Users can create and manage tasks for work and household activities, including due dates, priorities, and categories.
  
  \item Personalized recommendations: Machine learning models will analyze the user's task history and provide personalized recommendations for task prioritization and scheduling.
  
  \item REST API: A REST API will provide a connection between the frontend and backend components of the application.
  
  \item Apache Cassandra: A distributed NoSQL database system that provides scalability and performance for handling large amounts of data.
  
  \item Docker Compose: A tool for managing Docker containers, which provides scalability and manageability of the database cluster.
  
  \item TensorFlow: A popular open-source machine learning library that will be used to train the models for personalized recommendations.
\end{itemize}

Overall, this project aims to create a personalized and optimized task management experience for users, using the latest technologies in machine learning and AI.

\end{document}

